---
title: "Primer design - `r params$title`"
date: "`r params$date`"
output: html_document
params:
  date: NULL
  title: NULL
  settings: NULL
  varvamp_plots: NULL
  primer_df: NULL
  status_df: NULL

---

<style>
.main-container {
    max-width: 1500px;
    max-width: 100%;
    max-height: 1000px;
    margin-left: 5%;
    margin-right: 5%;
}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```


<!-- -------------------------------------------------------------------------------- -->

# varVamp primer design
```{r echo = FALSE, fig.align = 'center', out.width = "100%", results = 'asis'}
for (item in params$varvamp_plots){
   cat("![](", item, ")\n")  # Markdown syntax for embedding images
   cat('<br><br>')
}

```
The top figure depicts the calculated shannon entropies for each position in the alignment (grey) with rolling mean of window size 10 (black). Below are the different primer regions analyzed and generated by varVamp.


# Primer sets
<div align='center'>
```{r echo = FALSE, fig.align = 'center', out.width = "100%"}
params$primer_df
```

</div>
Overview of designed primers for each threshold used for varVamp.  Primers are named after primer pairs, therefore a primer sequence can have multiple primer names, if its mate is different. If there are multiple probes for a primer pair, they are designated as a, b, c, etc. 

<b>primer_name</b> - Name of primer. <b> seq </b> - primer sequence. <b>amp_name</b> - Name of primer pair/amplicon. <b>oligo_type</b> - Whether primer is left (forward), right (reverse) or probe. <b>primer_size</b> - Size of primer in nt. <b>start</b> - Start position in cleaned alignment. <b>stop</b> - Stop position in cleaned alignment. <b>ambig_count</b> - Number of ambiguous nucleotids in primer. <b>mean_gc</b> - Mean GC count of primer. <b>mean_temp</b> - Mean temp of primer. <b> penalty</b> - varVamp penalty score. <b>amp_len</b> - Length of primer amplicon. <b>threshold</b> - Consensus threshold used. <b>max_ambig</b> - Maximum allowed ambiguities in primer. Subtract 1 for probes. <b>note</b> - Comment. <b>off_targets</b> - Potential off-target hits (n.d. if not checked) <b>on_targets</b> - Potential on-target hits (n.d. if not checked). <b>on_target_fails</b> - List of targets that the primers failed against. Only the first 5 targets are listed in overview. 



# varVamp run status
<div align='center'>
```{r echo = FALSE, fig.align = 'center', out.width = "100%"}
params$status_df
```
</div>
Result of the different modes and parameters used to run varVamp.

## Settings

<div align='center'>
```{r echo = FALSE, fig.align = 'center'}
params$settings
``` 
</div>
Overview of settings used in the pipeline.
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
